---
title: "Schedule of Events"
---

::: {.callout-note appearance="simple" icon="false"}
## Note:

Talks will be held in the Ballroom A Posters will be displayed in the Ballroom B&C
:::

```{r echo=FALSE}
#| include: false


library(tidyverse)
library(kableExtra)

M <- read.csv('./generated/schedule.csv')
M_links <- read.csv('./generated/schedule_links.csv')

M$StartTime <- strftime(ymd_hms(M$StartTime), '%H:%M')
M$EndTime   <- strftime(ymd_hms(M$EndTime), '%H:%M')

M[(M$StartTime == M$EndTime), 'EndTime'] <- ''


subset_M <- function(x = "Wednesday, February 28, 2024"){
  out <- M |>
    filter(Day == x) |>
    left_join(rename(M_links, Link = Name), by = 'Link') |> 
    # mutate(Link = cell_spec(Link, 'html', link = Header)) |>
    mutate(Link = case_when(
      !is.na(Header) ~ cell_spec(Link, 'html', link = Header),
       is.na(Header) ~ Link)) |>
    select(StartTime, EndTime, Link, Presenter, Name, Location) |>
    rename(Start = StartTime, End = EndTime, Description = Name)
  return(out)
}


k <- function(x){
  x |> 
  kable('html', escape = FALSE) |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
}
```

## Wednesday, February 28, 2024



```{r echo=FALSE}
subset_M(x = "Wednesday, February 28, 2024") |> k()
```


## Thursday, February 29, 2024

```{r echo=FALSE}
subset_M(x = "Thursday, February 29, 2024")[1:9, ] |> k()
  
```


### SESSION 1 – WELCOME / FOSTERING DIVERSITY IN THE MAIZE COMMUNITY AND KEYNOTE SPEAKER

**Rubén Rellán Álvarez**


```{r echo=FALSE}
subset_M(x = "Thursday, February 29, 2024")[10:12, ] |> k()
```


```{r echo=FALSE}
subset_M(x = "Thursday, February 29, 2024")[13, ] |> k()
```



## Friday, March 1, 2024

```{r echo=FALSE}
subset_M(x = "Friday, March 1, 2024")[1:2, ] |> k()
```

### SESSION 2 – THE GENES THAT MAKE MAIZE

**Madelaine Bartlett**

```{r echo=FALSE}
subset_M(x = "Friday, March 1, 2024")[3:10, ] |> k()
```


### SESSION 3 – KEYNOTE  SPEAKER AND McCLINTOCK PRIZE PRESENTATION 

**Petra Wolters**

```{r echo=FALSE}
subset_M(x = "Friday, March 1, 2024")[11:14, ] |> k()
```


```{r echo=FALSE}
subset_M(x = "Friday, March 1, 2024")[15:20, ] |> k()
```


### SESSION 4 – NEW TOOLS AND RESOURCES I

**Lander Geadelmann**

```{r echo=FALSE}
subset_M(x = "Friday, March 1, 2024")[21:26, ] |> k()
```


### SESSION 5 – NEW TOOLS AND RESOURCES II   

**Graziana Taramino**

```{r echo=FALSE}
subset_M(x = "Friday, March 1, 2024")[27:33, ] |> k()
```


## Saturday, March 2, 2024

```{r echo=FALSE}
subset_M(x = "Saturday, March 2, 2024")[1:2, ] |> k()
```


### SESSION 6 – THE NITROGEN CONUNDRUM

**Frank Hochholdinger**

```{r echo=FALSE}
subset_M(x = "Saturday, March 2, 2024")[3:9, ] |> k()
```


### SESSION 7 – KEYNOTE SPEAKERS

**Hank Bass**

```{r echo=FALSE}
subset_M(x = "Saturday, March 2, 2024")[10:12, ] |> k()
```


```{r echo=FALSE}
subset_M(x = "Saturday, March 2, 2024")[13:23, ] |> k()
```


### SESSION 8 – MAIZE EVOLUTION

**Matthew Hufford**

```{r echo=FALSE}
subset_M(x = "Saturday, March 2, 2024")[24:28, ] |> k()
```


### SESSION 9 – ROOTS AND FRIENDS

**Stephanie Klein**

```{r echo=FALSE}
subset_M(x = "Saturday, March 2, 2024")[29:34, ] |> k()
```



## Sunday, March 3, 2024 


```{r echo=FALSE}
subset_M(x = "Sunday, March 3, 2024 ")[1, ] |> k()
```


### SESSION 10 – THE REGULATED GENOME

**Sarah Jensen**

```{r echo=FALSE}
subset_M(x = "Sunday, March 3, 2024 ")[2:7, ] |> k()
```


### SESSION 11 – METABOLIC REGULATION

**Sherry Flint-Garcia**

```{r echo=FALSE}
subset_M(x = "Sunday, March 3, 2024 ")[8:13, ] |> k()
```
